---
title: Umbrella for the alabaster framework
author:
- name: Aaron Lun
  email: infinite.monkeys.with.keyboards@gmail.com
package: alabaster
date: "Revised: January 18, 2023"
output:
  BiocStyle::html_document
vignette: >
  %\VignetteIndexEntry{alabaster umbrella}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo=FALSE}
library(BiocStyle)
self <- Githubpkg("ArtifactDB/alabaster.base");
knitr::opts_chunk$set(error=FALSE, warning=FALSE, message=FALSE)
```

# Motivation

This is an umbrella package for the **alabaster** framework that serves as an installation target to ensure that all (known) _alabaster.\*_ packages are installed.
Doing so is necessary because various functions in `r Githubpkg("ArtifactDB/alabaster.base")` dynamically identify the packages required to (un)serialize a particular resource.
By installing all _alabaster.\*_ packages at once, we ensure that the dynamic look-up does not fail due to a missing package.

This umbrella is only provided for convenient installation and is not otherwise necessary for the functioning of **alabaster** framework.
In fact, advanced users and package/application developers may prefer to install their required _alabaster.\*_ packages individually rather than relying on this umbrella.
This reduces the number of dependent packages that need to be installed, which is possible in scenarios where a limited subset of resource types are to be processed. 

# Session information {-}

```{r}
sessionInfo()
```

